Competing Bandits

### 2018-01-03 pres/pres.tex
final pres + writeup

@@

\item SoftMax is great!

@@

\item What if we made the rewards of the agents separate from the rewards of the principals?

>>>>

\item Unless specified otherwise, reported results found by averaging results from 25 simulations

@@

\item The logistic function takes the form \[f(x)=\epsilon + \frac{1-2\epsilon}{1+e^{-\alpha(x)}}\] where  $\epsilon$ controls the baseline probability each principal is chosen, and $\alpha$ controls the steepness of the curve. $x$ is the difference in score between the two principals. 
\item We set up a situation where a "smarter" algorithm starts at a disadvantage to a "dumber" algorithm due to different prior beliefs, and tune values of $\epsilon$ and $\alpha$ that result in the "smarter" algorithm winning
\item We settled on $\epsilon=0.05$ and $\alpha=10$ .

@@
